---
title: "AE05 - Git together"
date: "10/1/26"
format: html
execute:
  warning: false
  message: false
---

# Part 1: Working together on `main`

Team name: Team C for "Cool"

```{r icebreaker}
1 + 1
```

# Part 3: Collaborative Work

## Setup

```{r}
#| label: packages

library(tidyverse)
library(lubridate)
library(scales)
library(unvotes)

unv <- unvotes::un_votes %>%
  inner_join(un_roll_calls, by = "rcid") %>%
  inner_join(un_roll_call_issues, by = "rcid")
```

## Team questions

### Q1. How does one country vote?

Pick one country (check its spelling in the [AE01 Appendix](https://data385.netlify.app/ae/ae01-unvotes#appendix)) and make a bar chart of its `vote`s. Does it vote yes more often than no?

```{r}
unv  %>%
  filter(country == "United States") %>%
  ggplot(aes(x = vote, fill = vote)) +
  geom_bar() 
```

### Q2. What gets voted on the most?

Make a frequency table of `issue`. Which issue has the most votes?

```{r}
table(unv$issue)
```

The issue with the most votes is "Arms Control and Disarmament" with 170497 votes.

### Q3. U.S. yes votes by issue

For the United States, calculate the proportion of yes votes on each `issue`. Which issue does it vote yes on the most? The least?

```{r}

unv |>
  group_by(country, issue) |>
  filter(country == "United States") |>
  summarize(percent_yes = mean(vote == "yes")) |>
  arrange(desc(percent_yes))


```
It voted yes the most on Economic development (~28.2%) and the least on the Palestinian conflict (~10.6%)


### Q4. Two countries, one issue

Filter to the United States and Canada on "Human rights", then make a bar chart with one bar per `country`, filled by `vote` (`position = "fill"`). Do the two countries mostly agree?

```{r}
unv %>% 
  filter(country == c("United States", "Canada")) %>%
  group_by(issue == "Human Rights") %>%
  ggplot(aes(x = country, fill = vote)) +
  geom_bar(position = "fill") +
  labs(title = "Comparing Votes on Human Rights Issues", subtitle = "United States vs. Canada",
       y = "Votes", x = "Country")
```
No, the United States and Canada do not mostly agree on Human Rights issues. The United States has voted 'no' on Human Rights issues more than twice as much as Canada. Canada has also abstained from voting nearly twice as much as the United States. This indicates the two countries are very divided on Human Rights issues and disagree quite often.